Elaboration with First-Class Implicit Function Types

### 2020-02-25 paper.tex
stuff
stuff, nicer top lambda printing

\subsection{Contributions}
\begin{itemize}
  \item We propose an elaboration algorithm which translates from a small
    Agda-like surface language to a small Martin-L\"of type theory extended with
    implicit function types, telescopes and \emph{strictly curried function
      types} with telescope domain. We use these extensions to accummulate
    information about implicit insertions. Our algorithm is a conservative
    extension of Norell's bidirectional elaborator for Agda
    \cite[Chapter~3]{norell07thesis}.
  \item The presented elaborator is generally more powerful than previous
    solutions for impredicative inference. In particular, it goes beyond prior
    art by supporting full dependent type theory and by being global,
    i.e.\ inference may consider the whole program and not just particular n-ary
    applications.
  \item The target theory of elaboration serves as a general platform for
    elaborating implicit function types: our concrete elaborator is a relatively
    simple one, and there is room to further develop it.
  \item We provide an executable implementation of the elaborator described in
    this paper.
  \item Our solution is also \emph{simple}: we implemented elaboration,
    evaluation and unification in 650 lines of Haskell, of which about 200 lines
    implement the novel enhancements on the top of Norell's basic elaborator.
\end{itemize}

@@

It is implemented in 834 lines of Haskell. Of this, 660 lines constitute the
core syntax, evaluation, unification and elaboration. Of this 660 lines, 445
lines implement the basic elaborator of Section
\ref{sec:bidirectional_elaboration} and 215 lines implement the extended
elaborator. We give here implementation-specific details and describe
differences to the presentation in this paper.

>>>>

\subsection{Contributions}
\begin{itemize}
  \item We propose an elaboration algorithm which translates from a small
    Agda-like surface language to a small Martin-L\"of type theory extended with
    implicit function types, telescopes and \emph{strictly curried function
      types} with telescope domain. We use these extensions to accummulate
    information about implicit insertions. Our algorithm is a conservative
    extension of Norell's bidirectional elaborator for Agda
    \cite[Chapter~3]{norell07thesis}.
  \item The presented elaborator is generally more powerful than previous
    solutions for impredicative inference. In particular, it goes beyond prior
    art by supporting full dependent type theory and by being global,
    i.e.\ inference may consider the whole program and not just particular n-ary
    applications.
  \item The target theory of elaboration serves as a general platform for
    elaborating implicit function types: our concrete elaborator is a relatively
    simple one, and there is room to further develop it.
  \item We provide an executable implementation of the elaborator described in
    this paper.
  \item Our solution is also \emph{simple}: we implemented elaboration,
    evaluation and unification in about 670 lines of Haskell, of which 210 lines
    implement the novel enhancements on the top of Norell's basic elaborator.
\end{itemize}

@@

\todo{update loc}

It is implemented in about 1200 lines of Haskell. Of this, 673 lines constitute
the core syntax, evaluation, unification and elaboration. Of this 673 lines, 458
lines implement the basic elaborator of Section
\ref{sec:bidirectional_elaboration} and 215 lines implement the extended
elaborator. We give here implementation-specific details and describe
differences to the presentation in this paper.
